### 2014-01-27 brains-protocol.tex
Add FA description

Additional to classical psycholinguistic measures, we also considered more recently studied variables based on semantic network properties.
We relied on two types of network-based data: curated synonym associations provided by WordNet~\citep{WordNet10}, and ``free association'' relationships collected by~\citet{Nelson04}.

@@

\rk{Explain Free Association}

\TB{The original WN network is a weighted, undirected network; the FA network is a directed network where weights have a different meaning. Both semantic networks describe synonymy relationships corresponding to qualitatively distinct forms of association: either from a linguistic viewpoint (WN) or from the perspective of actual information retrieval by humans (FA).  In  order to work in a unified framework, we consider links as an information on the existence of some sort of association between two words and transform both networks into undirected, unweighed networks.} \rk{Check that's the case in the analysis}

>>>>

Additional to classical psycholinguistic measures, we also considered more recently studied variables based on semantic network properties.
We relied on two types of network-based data: curated synonym associations provided by WordNet~\citep{WordNet10}, and ``free association'' norms collected by~\citet{Nelson04}.

@@

Free Association (FA) norms record the words that come to mind when people are presented with a given cue (that is the ``free association'' task). As \citeauthor{Nelson04} explain,
\begin{quote}
free association response probabilities index the likelihood that one word can cue another word to come to mind with minimal contextual constraints in effect.~\citep{Nelson04}
\end{quote}
Following \citet{Griffiths07}, we consider the directed weighed network formed by the association norms, that is the network where words are nodes and edges are directed from cue to associated word, with a weight equal to the probability of that target word being produced when this particular cue was presented.

While the original WN network is a weighted, undirected network, the FA network is a directed network where weights have a different meaning.
Both semantic networks describe synonymy relationships corresponding to qualitatively distinct forms of association: either from a linguistic viewpoint (WN) or from the perspective of actual information retrieval by humans (FA).
In  order to work in a unified framework, we shall consider links as an information on the existence of some sort of association between two words and transform both networks into undirected, unweighed networks.
\rk{Check that's the case in the analysis}
